---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = F
)
library(tidyverse)
library(ggstamp)
```

# Introducing *{doublecrochet}*

```{r, warning=F, echo=F}
magick::image_read("https://images.unsplash.com/photo-1577635515158-dcce4789c8fb?ixlib=rb-1.2.1&ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&auto=format&fit=crop&w=751&q=80") %>% 
  magick::image_write(format = "png") %>% 
  ggbackdrop(png = .) +
  stamp_polygon(x0 = 82, y0 = 48, 
                radius = 15,
                fill = "brown",
                alpha = .2,
                size = 1.5,
                color = "oldlace",
                linetype = "dotted") + 
  stamp_text(label = "{doublecrochet}",
               fontface = "bold",
               x = 82, y = 48,
               size = 6, 
               color = "oldlace") + 
  stamp_label(label = ".Rmd source",
              fill = "oldlace",
              size = 7,
              x = 30, y = 30,
              color = "grey15") + 
  stamp_label(label = "output",
              fill = "oldlace",
              x = 60, y = 20,
              color = "grey15") + 
  stamp_tile(height = 60, width = 93, 
             x = 50, y = 33,
             alpha = 0, size = 2, 
             color = alpha("oldlace", .7)) +
  # stamp_text(label = ".Rmd ...", 
  #            size = 12, x = 18,
  #            y = 55, color = "oldlace",
  #            fontface = "bold", 
  #            family = "Times") +
  # stamp_text(label = "... together",
  #            size = 15, x = 70,
  #            y = 5, color = "oldlace",
  #            fontface = "italic") + 
  theme_void()
```




<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Rmarkdown files are so cool.  They let you to combine prose, code, and code output in a *single* output file.  And getting up and running with .Rmds is pretty easy --- learn bit about code chunks, a bit of markdown and you are good to go.  

But there is a lot that you can do in .Rmds beyond the basics. So you may feel .Rmd admiration and wonder at the products of more advanced users.  How did they to *that*?

Or maybe as an advanced user you might get asked:  *How did you produce those slides, poster, dashboard etc.?*  You can answer 'xaringan' or 'knitr', but can you deliver 'the how-to goods' in a detailed way when you get this question? (Another common sensation, looking back at your own work, may be 'how did I get that done?')

The goal of doublecrochet is to help produce a companion output from your .Rmd -- one that has .Rmd source snippets quoted close to the rendered output.

The package now focused a case where there are natural breakpoints -- slideshows!  Quoted source is presented on a slide, then the rendered content is shown. 

Check out doublecrochet's in action below. The first set of slides is a slide show of 'Cool Xaringan Stuff', and the second is the Double Crochetted version that quotes the slide source.

## *Compare* ...

### Cool Xaringan Stuff [Open in New tab](https://evamaerey.github.io/doublecrochet/cool_xaringan_stuff.html){target="_blank"}

<div style="position:relative;padding-top:56.25%;">
<iframe src="https://evamaerey.github.io/doublecrochet/cool_xaringan_stuff.html" frameborder="2" webkitallowfullscreen mozallowfullscreen allowfullscreen style="position:absolute;top:0;left:0;width:100%;height:100%;" allowtransparency="true">
</iframe>
</div>

## *... with the Double Crocheted version*  

### Cool Xaringan Stuff *Double Crocheted* [View in new tab](https://evamaerey.github.io/doublecrochet/cool_xaringan_stuff_double_crochet.html){target="_blank"}:

<div style="position:relative;padding-top:56.25%;">
<iframe src="https://evamaerey.github.io/doublecrochet/cool_xaringan_stuff_double_crochet.html" frameborder="2" webkitallowfullscreen mozallowfullscreen allowfullscreen style="position:absolute;top:0;left:0;width:100%;height:100%;" allowtransparency="true">
</iframe>
</div>

## Motivation

Inspiration for this project was creating [Easy Flipbooks Recipes](https://evamaerey.github.io/flipbooks/flipbook_recipes#1) where I was quoting my source a bunch w/ copy paste and fancy fencing. I only got through 4 'recipes'.  But there were more 'recipes' that I'd like to share.  

Having 'doublecrochet' working should be nice for communicating about how to use flipbookr -- and other cool xaringan-complementary packages. 

2022 update: Now quoting the .Rmd verbatim is done using the new [verbatim engine](https://yihui.org/en/2022/01/knitr-news/) from knitr! 



## Installation

<!-- You can install the released version of doublecrochet from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("doublecrochet") -->
<!-- ``` -->

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("EvaMaeRey/doublecrochet")
```
## Example

For now doublecrochet::crochet() is intended for use with xaringan .Rmd slide show files:

```{r example, eval = F}
library(doublecrochet)

## a text .rmd file stored on github
download.file(
  url = "https://raw.githubusercontent.com/EvaMaeRey/doublecrochet/master/inst/rmarkdown/templates/double-crochet/skeleton/skeleton.Rmd", 
  destfile = "docs/cool_xaringan_stuff.Rmd")

# regular render of xaringan .Rmd 
rmarkdown::render(input = "docs/cool_xaringan_stuff.Rmd")

# double crochet render
doublecrochet::crochet(input = "docs/cool_xaringan_stuff.Rmd", render = T)
                      

```

Once you have the 'doublecrochet' version of your .Rmd, you can try to compile and render this and you'll have html output.  Source will be quoted throughout. 

````{comment}
## Bugs

Backslashing is still being worked out.  Especially sad is that math mode doesn't work well because of this.  :-(  I see this "--from markdown+autolink_bare_uris+tex_math_single_backslash" in pandoc conversion upon render.  Maybe the answer is in there...

We see this with the xaringan template below.

```{r buggs, eval = F}
library(doublecrochet)

download.file("https://raw.githubusercontent.com/yihui/xaringan/master/inst/rmarkdown/templates/xaringan/skeleton/skeleton.Rmd", "xaringan_skeleton.Rmd")

doublecrochet::doublecrochet("xaringan_skeleton.Rmd")

# fails!  you've got to go into the .Rmd and fix up backslashes

# in fact for the math type the conversion is not working, you have to go back in and escape
# rmarkdown::render("xaringan_skeleton_double_crochet.Rmd")
```

````

## Scope

Doublecrochet doesn't do a good job of showing bigger picture and global style changes in a file.  


