---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# doublecrochet

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Rmarkdown files are super cool because they allow you to co-mingle prose, code, and output in a single output file.  Having code and code output proximate in a rendered document is helpful at interpreting intent of the code.  And getting up and running with .Rmds is pretty easy --- learn about code chunks, learn a bit of markdown and you are good to go.  

But there is a lot that you can do in .Rmds beyond the basics. One can quickly experience .Rmd envy when seeing the products of more advanced users.  

And as you become a more advanced user you might asked more and more:  How did you produce those slides, poster, dashboard etc.?  How can you easily deliver 'the how-to goods' in a detailed way when you get this question?

**The goal of doublecrochet is to help you produce a second output from your .Rmd -- one that has source snippets quoted proximate (usually prior) to the rendered output.**

The package is experimental, and now focused a case where there are natural breakpoints -- slideshows!  Quoted source is be presented on a slide, then the rendered content is shown. Yay!

Inspiration for this project was creating [Easy Flipbooks Recipes](https://evamaerey.github.io/flipbooks/flipbook_recipes#1) where I was quoting my source a bunch w/ copy paste and fancy fencing.  But it was painstaking and error prone, and I only got through 4 recipes.  But there are more 'recipes' that I'd like to share.  One test/usecase will be 'Most Flipbookr Features' template, a template that is part of the flipbookr package that demonstrates (and I use for testing) most flipbookr modes. Having 'doublecrochet' working should be nice for communicating about how to use flipbookr -- and other cool xaringan-complementary packages. Meanwhile, we'll think about how it can be used for other .Rmd products where we don't have slide breaks as natural pause points.


## Installation

<!-- You can install the released version of doublecrochet from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("doublecrochet") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("EvaMaeRey/doublecrochet")
```
## Example

For now doublecrochet::crochet() is intended for use with xaringan .Rmd slide show files:

```{r example, eval = F}
library(doublecrochet)

## a text .rmd file stored on github
my_rmd <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/minimal-flipbook/skeleton/skeleton.Rmd"

## translating to the _double version
crochet(my_rmd, output = "my_rmd_double.Rmd")
```

Once you have the 'doublecrochet' version of your .Rmd, you can compile and render this and you'll have html output w source quoted throughout.  
